Universal Anonymous Signatures

### 2022-08-17 prism-backend/research/gsac/relationships.tex
Finishing pass.

\begin{figure}[ht!]

  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
      \textbf{Issuance functions:}
      \begin{align}
        & \fissue^1(\cdot,\cdot,\cdot) \coloneqq 1 \nonumber \\
        & \fissue^{single,F,I}(\upk,\cdot,\cdot) \coloneqq \pcreturn
          F(I,\upk)
          \nonumber \\
        & \fissue^{\sring}(\upk,\cdot,\attrs) \coloneqq
          \pcreturn (\attrs = \sring \land \upk \in \attrs) \nonumber
      \end{align}

      \textbf{Signature evaluation functions:}
      \begin{align}
        & \feval^0(\cdot,\cdot,\cdot) \coloneqq \pcreturn (0,\ast) \nonumber \\
        & \feval^{\dattrs}(\cdot,(\cdot,\attrs),\cdot)
          \coloneqq \pcreturn (\lbrace \attrs_i \rbrace_{i\in \dattrs},\ast)
          \nonumber \\
        & \feval^{\sring,\dattrs}(\upk,(\cdot,\attrs),\cdot)
          \coloneqq \pcif \upk \in \lbrace \attrs_i \rbrace_{i\in\dattrs}
          \subseteq \sring:
          \pcreturn (\lbrace \attrs_i \rbrace_{i\in\dattrs},\ast);
          \pcelse \pcreturn (0,\ast) \nonumber \\
        & \feval^{\dattrs,F,V,L}(\upk,((\cidi,\cidu),\attrs),\cdot) \coloneqq
          \nonumber \\
        & \hspace*{2em}\pcif F(V,\cidi) \in L \lor F(V,\cidu) \in L:
          \pcreturn (0,\ast) \nonumber \\
        & \hspace*{2em}\pcelse \pcreturn (\lbrace \attrs_i \rbrace_{i\in \dattrs},V)
          \nonumber \\
        & \feval^{g,MPS}(\upk,\lbrace (\cid_i,\attrs_i) \rbrace_{i\in[n]},\msg)
          \coloneqq \nonumber \\
        & \hspace*{2em}\pcif g(\upk,\lbrace (\cid_i,\attrs_i) \rbrace_{i\in[n]},
          \msg) = 0: \pcreturn \bot \nonumber \\
        & \hspace*{2em}\pcelse \pcreturn (\ast,g(\upk,\lbrace
          (\cid_i,\attrs_i) \rbrace_{i\in[n]},\msg)) \nonumber
      \end{align}
    \end{minipage}
  }
  \vspace*{1em}

  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
      \textbf{Open functions:}
      \begin{align}
        & \finsp^0(\cdot,\cdot,\cdot,\cdot) \coloneqq 0 \nonumber \\
        & \finsp^{\upk}(\cdot,\upk,\cdot,\cdot) \coloneqq
          \pcreturn \upk % \CCommit(\usk;0)
          \nonumber \\
        & \finsp^{F}((\yeval^0,\yeval^1),\cdot,((\cidi,\cidu),\attrs),\cdot)
          \coloneqq \nonumber \\
        & \hspace*{2em}\pcif \yeval^0 \neq 0:
          \pcreturn (F(\yeval^1,\cidi),F(\yeval^1,\cidu)) \nonumber \\
        & \hspace*{2em}\pcelse \pcreturn 0
          \nonumber \\
        & \finsp^{h,MPS}((\cdot,\yeval^1),\upk,\cid,\attrs,\cdot) \coloneqq
          \pcreturn h(\yeval^1,\upk,\cid,\attrs) \nonumber         
      \end{align}
    \end{minipage}
    \hspace*{5em}
    % \begin{minipage}[t]{0.47\textwidth}
    %   \begin{framed}
    %     $\attrs(\cred)$ returns all attributes in \cred \\
    %     $\dattrs(\cred)$ returns $\dattrs \subseteq \attrs(\cred)$ \\
    %     $\attrs_i(\cred)$ returns $i$-th attribute in \cred \\
    %     $\ast$ means the output is ignored \\
    %     $\bot$ means the function fails
    %   \end{framed}
    % \end{minipage}
  }
  \caption{Functions for the \CUASGen restrictions described next.
    For readability, we use ``$\cdot$'' to denote input arguments that are
    ignored; and ``$\ast$'' to denote output values that can be set to anything
    (but should be ignored). $\bot$ means that the function fails.}
  \label{fig:func-restrictions}
\end{figure}

@@

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.55\textwidth}        
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,rs}(1^\secpar)$}{%
        ((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar) \\
        (i_0,i_1,R,\msg,\st) \gets \adv^{SIGN}(\pk_1,\dots,\pk_n) \\
        \pcif R \not\subseteq \lbrace \pk_i \rbrace_{i\in[n]} \lor
        \lbrace \pk_{i_0},\pk_{i_1} \rbrace \not\subseteq R~\lor \\ %\\
        \pcind i_0 = i_1: \pcreturn \bot \\
        \sig \gets Sign(\sk_{i_b},R,\msg) \\
        b^* \gets \adv(\sig,\st) \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.5\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,rs}(1^\secpar)$}{%
        ((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar) \\
        (R,\sig,\msg) \gets \adv^{SIGN,CORR}(\pk_1,\dots,\pk_n) \\
        \pcif Verify(R,\sig,\msg) = 0: \pcreturn 0 \\
        \pcreturn (R \subseteq \lbrace \pk_i \rbrace_{i\in[n]} \setminus
        CU~\land \\
        \pcind \adv~\textrm{never queried}~SIGN(\cdot,R,\msg))
      }       
    \end{minipage}      
  }
  \caption{Security games for ring signatures \cite{bkm06}. The $SIGN$ oracle
    accepts $(i,R,\msg)$ tuples, with $pk_i \in R$, adds the tuple to a list of
    queries, and returns $\sig \gets Sign(\sk_i,R,\msg)$. $CORR$
    accepts an index $i$, and leaks $\sk_i$ to $\adv$. Corrupted users are added
    to $CU$.}
  \label{fig:model-rs}  
\end{figure}

@@

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.5\textwidth}        
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,ac}(1^\secpar)$}{%
 %       \parm \gets \Setup(1^\secpar) \\
        (\ipk,\isk) \gets IssKeyGen(1^\secpar) \\        
        b^* \gets \adv^{HU,CU,Obtain,Show,LoR}(\isk) \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.5\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,ac}(1^\secpar)$}{%
%        \parm \gets \Setup(1^\secpar) \\
        (\ipk,\isk) \gets IssKeyGen(1^\secpar) \\        
        (D,\st) \gets \adv^{HU,CU,ObtIss,Issue,Show}(\ipk) \\
        \langle \cdot,(b,\utrans) \rangle
        \gets \langle \adv(\st),\Verify(\ipk,D) \rangle \\
        \pcreturn (b = 1 \land \nexists j~\suchthat \\
        \pcind (\OWNR[j] \in \CU
        \land D \subseteq \ATTR[j])) % \forall j, \OWNR[j] \in \CU
        % \implies D \not\subseteq \ATTR[j]: \\
        %\pcind \pcreturn 1 \\
        %\pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for anonymous credentials with selective disclosure
    \cite{fhs19}. \OWNR and \ATTR tables are essentially as in \UAS. \adv~wins
    the unforgeability game if it authenticates successfully while revealing
    attributes not contained in adversarially controlled credentials. All
    oracles in this model have a direct equivalent in \UAS.
  }
  \label{fig:model-ac}  
\end{figure}

@@

\begin{description}
% \item[$\parm \gets \Setup(1^\secpar)$.] Runs $\parm' \gets \Setup(1^\secpar,
%   \AttrSpace)$ and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our
%   \CUASGen construction. Returns $\parm \gets (\parm',\opk)$.
\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] From $\CUASGen^{int}$, run $\parm'
  \gets \Setup(1^\secpar)$ and $(\opk,\osk) \gets \OKeyGen(\parm',
  \finsp^0)$, and set $\parm \gets (\parm',\opk)$. Run $(\upk,\usk) \gets
  \KeyGen(\parm')$ and $\ipk \gets \ISet(\upk,\usk,\fissue^1)$. Set $\isk \gets
  \usk$.
\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \KeyGen from $\CUASGen^{int}$.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
  Runs $\langle \Obtain,\Issue \rangle$ from $\CUASGen^{int}$.
\item[$\langle 1/0,((1,\utrans)/(0,\utrans)\rangle
  \gets \langle Show(\ipk,\attrs,\dattrs,
  \cred),\Verify(\ipk,\dattrs) \rangle$.]
  Runs the interactive transform of \Sign and \Verify of $\CUASGen^{int}$, using
  $\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as open
  function, with \opk from \parm as opener public key.
\end{description}

@@

In \cite{cks10}, revocable anonymous credentials are proposed. From \CUASGen, it
is straightforward to build an AC system with verifier local revocation, like in
\cite{bs04}. Basically, we leverage the $\cid=(\cidi,\cidu)$ identifiers,
encoded as attributes, to define a $(\feval,\finsp)$ function pair that: (1)
ensures that opening outputs the evaluation of a PRF of the {\cid}s concatenated
with the verifier name; and (2) ensures that, if some {\cid} of the credentials
used to produce a signature have been added to a revocation list by the
verifier, the verifier will know it -- and hence will be able to reject the
signature. We first give a simple model in
\figref{fig:model-rac}, extending that in \secref{ssec:related-models-ac}.
Concretely, to the functionality in \secref{ssec:related-models-ac}, we now
explicitly add
the $OKeyGen$ function (equivalent to \OKeyGen, with a fixed \finsp function),
which generates the opener key pair, extend $Verify$ to receive also a list $L$
of revoked credential identifiers, and we add a function (and corresponding
oracle) $cid/\bot \gets RetrieveCredId(\osk,\utrans)$ that can extract an
identifier of the credential used in a presentation transcript \utrans -- and
which is essentially equivalent to \Open in \UAS. For simplicity, we do not
include the equivalent to verifiable openings, but this would be
straightforward.

@@

\subsubsection{\CUASRAC Construction.} %
Briefly, we build a revocable anonymous credential as a $(\fissue^1,
\feval^{\dattrs,F,V,L},\finsp^{F})$-\CUASGen restriction. \feval is
parameterized with a PRF $F$, a string identifying the verifier $V$ and a
list $L$ of ``revocation handles'' by $V$. Note that these can be hardcoded,
though: $F$ can be common to all verifiers, $V$ is also fixed (per verifier),
and $L$ can be updated with some reasonable frequency -- e.g., daily -- so that
the cost of recomputing $\feval^{\dattrs,F,V,L}$ is not high.
%
Since credentials in \CUASGen have two identifiers (\cidi, chosen by the issuer;
and \cidu, chosen by the user), $\feval^{\dattrs,F,V,L}$ internally computes
$F(V,\cidi)$ and $F(V,\cidu)$. If either appears in $L$, \feval sets $\yeval^0$
to $0$, which the verifier interprets as ``revoked credential''. Otherwise,
it sets $\yeval^0 \gets \lbrace \attrs_i \rbrace_{i\in\dattrs}$ and
$\yeval^1 \gets V$. $\yeval^1$ is
then used by $\finsp^F$ to compute $\yinsp \gets (F(\yeval^1,\cidi),
F(\yeval^1,\cidu))$. Thus, if the verifier $V$ wants to revoke a credential, all
it has to do is ask the opener to decrypt $\yinsp$, via $RetrieveCredHandle$.
%
In more detail, the algorithms are as follows:

\begin{description}
\item[$\parm \gets \Setup(1^\secpar)$.] Runs $\Setup(1^\secpar)$ as in
  \CUASGen.
\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \KeyGen+\ISet from our
  \CUASGen construction, setting $\fissue^1$ as issuance function.
\item[$(\ipk,\isk) \gets OKeyGen(\parm)$.] Runs \OKeyGen from our
  \CUASGen construction, setting $\finsp^F$ as opening function.
\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \KeyGen from the
  \CUASGen construction.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGen, using
  $\fissue^1$ as issuance function.
\item[$\langle 1/0,(1,\utrans)/(0,\utrans)\rangle \gets \langle Show(\ipk,
  \attrs,\dattrs,\cred),
  \Verify(\ipk,\dattrs) \rangle$.]
  Runs the interactive extension of \Sign and \Verify of the \CUASGen protocol,
  using $\feval^{\dattrs,F,V,L}$ as signature evaluation function, and
  $\finsp^F$ as open function. If $\yeval^0 = 0$, the signature is rejected.
\item[$h/\bot \gets RetrieveCredHandle(\osk,\utrans)$.]
  Gets $(\sig,\yeval^0)$ from the $\langle Show,\Verify\rangle$ transcript
  \utrans, and runs \Open from \CUASGen. If $\yeval^0 \neq 0$ (i.e., the
  signature was created by a non-revoked credential), this returns $(F(V,\cidi),
  F(V,\cidu))$, which the verifier can add to its revocation list $L$.
\end{description}

@@

\begin{theorem}[Anonymity of \CUASRAC]
  If the base \CUASGen construction has signature anonymity according to
  \defref{def:sign-anonymity-uas}, and $F$ is one-way, then \CUASRAC is an
  anonymous AC scheme according to \cite{fhs19}.  
\end{theorem}

\begin{theorem}[Unforgeability of \CUASRAC]
  If the base \CUASGen construction is unforgeable according to
  \defref{def:forge-uas}, and $F$ is one-way, then \CUASRAC is an unforgeable
  RAC scheme.
\end{theorem}

Note that, if we aim at global credential (resp. user) revocation rather than
verifier-local revocation, we can have \finsp just output the $(\cidi,\cidu)$
pair (resp., \upk), and no assumption regarding $F$ is needed.

@@

Multimodal Private Signatures (or, rather, a close relative, see next) are
directly implementable as a $(\fissue^{single,F,I},\feval^{\yeval^1},
\finsp^{\ast})$-\CUASGen restriction, where $\feval^{\yeval^1}$ is any signature
evaluation function that ignores the $\yeval^0$ output, and $\finsp^{\ast}$ is
any open function. Concretely, this restricts to a system with one issuer and
one opener, one credential per user, no attributes in the credentials.

There are some differences, though. On the one hand, our signature anonymity
property is somehow in the middle of MPS's privacy-1 and privacy-2 variants.
Their privacy-1 variant is the traditional anonymity property of group
signatures, in which the opener is honest and the adversary can call the opening
oracle except for challenge signatures. In their privacy-2 variant, the opener
is fully corrupt (i.e., \adv~ receives \osk), but the adversary can only be
challenged with signatures that produce the same \yinsp value ($G_{j_b}(id_b)$
in MPS). In our \UAS model, we allow the adversary to corrupt openers at will
(getting ther \osk), but the challenge signatures must have been generated using
the key of an uncorrupted opener; still, \adv~can call the open oracle for
challenge signatures, as long as they have the same \yinsp value. We believe
that these differences are mostly of theoretical interest, though. In practice,
what matters is that any variant of \feval and \finsp functions ($F$ and $G_j$
in MPS) that has too much granularity in their ranges, will lead to a barely
private system. This is a known issue, for instance, in functional encryption
\needcite.

On the other hand, anonymous issuance, and the capability to customize issuance
policies are unachievable by MPS. Anonymous issuance simply does not make sense
in MPS, as it only supports one credential (without attributes) per user.
Customized issuance is achieved in \UAS via the \fissue functions, with no
equivalent in MPS -- instead, MPS has the fixed policy of
``proving knowledge of a user secret key''. These extensions are not trivial
from a theoretical point of view, and also have a big impact in the practicality
of the resulting system. Also, MPS does not include verifiable openings. While
this is easy to add, we consider it to be essential, given that the proposed
generalization of opening allows the opener to output ``any value''. Hence, the
need to ensure that the produced value is the legitimate one, seems to be more
necessary than ever. Finally, our \feval function is a generalization of $F$ in
MPS, as it allows two outputs: one will be returned in the clear along with the
signature, and the other will be encrypted. Still both computations are proved
correct. Making part of the output unencrypted allows implementing very useful
variants such as anonymous credentials, as shown before.

@@

\subsubsection{\CUASMPS construction.} %
As mentioned, any $(\fissue^{single,F,I},\feval^{\yeval^1},
\finsp^\ast)$-restriction implements an MPS scheme where $F=\feval^{\yeval^1}$
and $G=\finsp^\ast$. With these functions, the construction is direct.
\CUASMPS's setup runs \CUASGen's \Setup, \OKeyGen, and generates the issuer key
pair by running \KeyGen and \ISet (with $\fissue^1$). For MPS's join, \CUASMPS
runs first \KeyGen to generate the user key pair, and then proceeds as in
\CUASGen. \Sign, \Verify and \Open, are as in \CUASGen.
%
Finally, note that, in MPS, $G$ is further parameterized with a value $j$, which
essentially is the result of applying $F$ to the message and signer identity,
and is not leaked to the opener nor any other third party. The equivalent in
\UAS is the $\yeval^1$ value which, in \CUASGen, is encrypted with a single-use
key pair, and is an input of \yinsp.

@@

\begin{theorem}[Unforgeability-1 of \CUASMPS]
  If the base \CUASGen construction is unforgeable according to
  \defref{def:sign-forge-uas}, then \CUASMPS satisfies unforgeability-1 as
  defined in \cite{ngsy22}.
\end{theorem}

>>>>

\begin{figure}[ht!]
  \input{figures/functions.tex}
  \caption{Functions for the \CUASGen restrictions described next.
    For readability, we use ``$\cdot$'' to denote input arguments that are
    ignored; and ``$\ast$'' to denote output values that can be set to anything
    (but should be ignored). $\bot$ means that the function fails.}
  \label{fig:func-restrictions}
\end{figure}

@@

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.55\textwidth}        
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,rs}(1^\secpar)$}{%
        ((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar) \\
        (i_0,i_1,R,\msg,\st) \gets \adv^{SIGN}(\pk_1,\dots,\pk_n) \\
        \pcif R \not\subseteq \lbrace \pk_i \rbrace_{i\in[n]} \lor
        \lbrace \pk_{i_0},\pk_{i_1} \rbrace \not\subseteq R~\lor \\ %\\
        \pcind i_0 = i_1: \pcreturn \bot \\
        \sig \gets Sign(\sk_{i_b},R,\msg) \\
        b^* \gets \adv(\sig,\st) \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.5\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,rs}(1^\secpar)$}{%
        ((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar) \\
        (R,\sig,\msg) \gets \adv^{SIGN,CORR}(\pk_1,\dots,\pk_n) \\
        \pcif Verify(R,\sig,\msg) = 0: \pcreturn 0 \\
        \pcreturn (R \subseteq \lbrace \pk_i \rbrace_{i\in[n]} \setminus
        CU~\land \\
        \pcind \adv~\textrm{never queried}~SIGN(\cdot,R,\msg))
      }       
    \end{minipage}      
  }
  \caption{Security games for ring signatures \cite{bkm06}. The $SIGN$ oracle
    accepts $(i,R,\msg)$ tuples, with $pk_i \in R$, adds the tuple to a list of
    queries, and returns $\sig \gets Sign(\sk_i,R,\msg)$. $CORR$
    accepts an index $i$, and leaks $\sk_i$. Corrupted users are added
    to $CU$.}
  \label{fig:model-rs}  
\end{figure}

@@

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.5\textwidth}        
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,ac}(1^\secpar)$}{%
 %       \parm \gets \Setup(1^\secpar) \\
        (\ipk,\isk) \gets IssKeyGen(1^\secpar) \\        
        b^* \gets \adv^{HU,CU,Obtain,Show,LoR}(\isk) \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.5\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,ac}(1^\secpar)$}{%
%        \parm \gets \Setup(1^\secpar) \\
        (\ipk,\isk) \gets IssKeyGen(1^\secpar) \\        
        (D,\st) \gets \adv^{HU,CU,ObtIss,Issue,Show}(\ipk) \\
        \langle \cdot,(b,\utrans) \rangle
        \gets \langle \adv(\st),\Verify(\ipk,D) \rangle \\
        \pcreturn (b = 1 \land \nexists j~\suchthat \\
        \pcind (\OWNR[j] \in \CU
        \land D \subseteq \ATTR[j])) % \forall j, \OWNR[j] \in \CU
        % \implies D \not\subseteq \ATTR[j]: \\
        %\pcind \pcreturn 1 \\
        %\pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Games for anonymous credentials with selective disclosure
    \cite{fhs19}. \OWNR, \ATTR, and the oracles, are essentially as in
    \UAS. \adv~wins $\Exp^{forge}_{\adv,ac}$ if it authenticates successfully
    while revealing attributes not contained in adversarially controlled
    credentials.}
  \label{fig:model-ac}  
\end{figure}

@@

\begin{description}
% \item[$\parm \gets \Setup(1^\secpar)$.] Runs $\parm' \gets \Setup(1^\secpar,
%   \AttrSpace)$ and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our
%   \CUASGen construction. Returns $\parm \gets (\parm',\opk)$.
\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] From $\CUASGen^{int}$, run $\parm'
  \gets \Setup(1^\secpar)$ and $(\opk,\osk) \gets \OKeyGen(\parm',
  \finsp^0)$, and set $\parm \gets (\parm',\opk)$. Run $(\upk,\usk) \gets
  \KeyGen(\parm')$ and $\ipk \gets \ISet(\upk,\usk,\fissue^1)$. Set $\isk \gets
  \usk$.
\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \KeyGen from $\CUASGen^{int}$.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
  Runs $\langle \Obtain,\Issue \rangle$ from $\CUASGen^{int}$.
\item[$\langle 1/0,((1,\utrans)/(0,\utrans)\rangle
  \gets \langle Show(\ipk,\attrs,\dattrs,
  \cred),\Verify(\ipk,\dattrs) \rangle$.]
  Runs the interactive $\langle \Sign, \Verify\rangle$ of  $\CUASGen^{int}$,
  using $\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as
  open function, with \opk from \parm as opener public key.
\end{description}

@@

In \cite{cks10}, revocable anonymous credentials are proposed. We first give a
simple model in \figref{fig:model-rac}, extending that in
\secref{ssec:related-models-ac}. Concretely, to the functionality in
\secref{ssec:related-models-ac}, we now explicitly add the $OKeyGen$ function,
which generates the opener key pair, extend $Verify$ to receive also a list $L$
of revoked credential identifiers, and we add a function (and corresponding
oracle) $cid/\bot \gets RetrieveCredId(\osk,\utrans)$ that can extract an
identifier of the credential used in a presentation transcript \utrans. For
simplicity, we do not include the equivalent to verifiable openings, but this
would be straightforward.

@@

\subsubsection{\CUASRAC Construction.} %
Briefly, this is achieved via a $(\fissue^1,\feval^{\dattrs,F,V,L},
\finsp^{F})$-$\CUASGen^{int}$ restriction. \feval is parameterized with a PRF
$F$, a string identifying the verifier $V$ and a list $L$ of ``revocation
handles'' by $V$. Note that these can be hardcoded, though: $F$ can be common to
all verifiers, $V$ is also fixed (per verifier),
and $L$ can be updated with some reasonable frequency -- e.g., daily -- so that
the cost of recomputing $\feval^{\dattrs,F,V,L}$ is not high.
%
Since credentials in $\CUASGen^{int}$ have two identifiers (\cidi, chosen by the
issuer; and \cidu, chosen by the user), $\feval^{\dattrs,F,V,L}$ internally
computes $F(V,\cidi)$ and $F(V,\cidu)$. If either appears in $L$, \feval sets
$\yeval^0$ to $0$, which the verifier interprets as ``revoked credential''.
Otherwise, it sets $\yeval^0 \gets \lbrace \attrs_i \rbrace_{i\in\dattrs}$ and
$\yeval^1 \gets V$. $\yeval^1$ is
then used by $\finsp^F$ to compute $\yinsp \gets (F(\yeval^1,\cidi),
F(\yeval^1,\cidu))$. Thus, if the verifier $V$ wants to revoke a credential, all
it has to do is ask the opener to decrypt $\yinsp$, via $RetrieveCredHandle$.
%
In more detail, the algorithms are as follows:

\begin{description}
\item[$\parm \gets \Setup(1^\secpar)$.] Runs $\Setup(1^\secpar)$ as in
  \CUASGen.
\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \KeyGen+\ISet from our
  $\CUASGen^{int}$ construction, setting $\fissue^1$ as issuance function.
\item[$(\ipk,\isk) \gets OKeyGen(\parm)$.] Runs \OKeyGen from our
  $\CUASGen^{int}$ construction, setting $\finsp^F$ as opening function.
\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \KeyGen from the
  $\CUASGen^{int}$ construction.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGen, using
  $\fissue^1$ as issuance function.
\item[$\langle 1/0,(\dattrs,\utrans)/(0,\utrans)\rangle \gets \langle Show(\ipk,
  \attrs,\dattrs,\cred),
  \Verify(\ipk,\dattrs) \rangle$.]
  Runs the interactive $\langle\Sign,\Verify\rangle$ of $\CUASGen^{int}$,
  using $\feval^{\dattrs,F,V,L}$ as signature evaluation function, and
  $\finsp^F$ as open function. The \dattrs value output by the verifier is
  the $\yeval^0$ value produced by \Sign (when accepted by \Verify).
\item[$h/\bot \gets RetrieveCredHandle(\osk,\utrans)$.]
  Gets $(\sig,\yeval^0)$ from the $\langle Show,\Verify\rangle$ transcript
  \utrans, and runs \Open from $\CUASGen^{int}$. If $\yeval^0 \neq 0$ (i.e., the
  signature was created by a non-revoked credential), this returns $(F(V,\cidi),
  F(V,\cidu))$, which the verifier can add to its revocation list $L$.
\end{description}

@@

\begin{theorem}[Anonymity of \CUASRAC]
  If the base $\CUASGen^{int}$ construction has signature anonymity according to
  \defref{def:sign-anonymity-uas}, and $F$ is one-way, then \CUASRAC is an
  anonymous AC scheme according to \cite{fhs19}.  
\end{theorem}

\begin{theorem}[Unforgeability of \CUASRAC]
  If the base $\CUASGen^{int}$ construction is unforgeable according to
  \defref{def:forge-uas}, and $F$ is one-way, then \CUASRAC is an unforgeable
  RAC scheme.
\end{theorem}

% Note that, if we aim at global credential (resp. user) revocation rather than
% verifier-local revocation, we can have \finsp just output the $(\cidi,\cidu)$
% pair (resp., \upk), and no assumption regarding $F$ is needed.

@@

Multimodal Private Signatures (or, rather, a close relative, see next) are
directly implementable as a $(\fissue^{single,F,I},\feval^{g,MPS},
\finsp^{h,MPS})$-\CUASGen restriction. Concretely, this restricts to a system
with one credential per user and no attributes in the credentials.

There are some differences, though. On the one hand, our signature anonymity
property is somehow in the middle of MPS's privacy-1 and privacy-2 variants.
Their privacy-1 variant is the traditional anonymity property of group
signatures, in which the opener is honest and the adversary can call the opening
oracle except for challenge signatures. In their privacy-2 variant, the opener
is fully corrupt (i.e., \adv~ receives \osk), but the adversary can only be
challenged with signatures that produce the same \yinsp value ($G_{j_b}(id_b)$
in MPS). In our \UAS model, we allow the adversary to corrupt openers at will
(getting ther \osk), but the challenge signatures must have been generated using
the key of an uncorrupted opener; still, \adv~can call the open oracle for
challenge signatures, as long as they have the same \yinsp value. We believe
that these differences are mostly of theoretical interest, though. In practice,
what matters is that any variant of \feval and \finsp functions ($F$ and $G_j$
in MPS) that has too much granularity in their ranges, will lead to a barely
private system. This is a known issue, for instance, in functional encryption
\cite{bsw11}.

On the other hand, anonymous issuance and the capability to customize issuance
policies are unachievable by MPS. Anonymous issuance simply does not make sense
in MPS, as it only supports one credential (without attributes) per user, and
customized issuance is achieved in \UAS via the \fissue functions, with no
equivalent in MPS -- instead, MPS has the fixed policy of
``proving knowledge of a user secret key''. These extensions are not trivial
from a modelling point of view, and also have a big impact in the practicality
of the resulting system. Also, MPS does not include verifiable openings. While
this is easy to add, we consider it to be essential, given that the proposed
generalization of opening allows the opener to output ``any value''. Hence, the
need to ensure that the produced value is the legitimate one, seems to be more
necessary than ever. Finally, our \feval function is a generalization of $F$ in
MPS, as it allows two outputs: one will be returned in the clear along with the
signature, and the other will be encrypted. Indeed, making part of the output
unencrypted allows implementing very useful variants such as anonymous
credentials, as shown before.

@@

\subsubsection{\CUASMPS construction.} %
As mentioned, any $(\fissue^{single,F,I},\feval^{g,MPS},
\finsp^{h,MPS})$-restriction implements an MPS scheme where $F=\feval^{\yeval^1}$
and $G=\finsp^\ast$. With these functions, the construction is direct.
\CUASMPS's setup runs \CUASGen's \Setup, \OKeyGen, and generates the issuer key
pair by running \KeyGen and \ISet (with $\fissue^1$). For MPS's join, \CUASMPS
runs first \KeyGen to generate the user key pair, and then proceeds as in
\CUASGen. \Sign, \Verify and \Open, are as in \CUASGen.
%
Finally, note that, in MPS, $G$ is further parameterized with a value $j$, which
essentially is the result of applying $F$ to the message and signer identity,
and is not leaked to the opener nor any other third party. The equivalent in
\UAS is the $\yeval^1$ value which, in \CUASGen, is encrypted with a single-use
key pair, and is an input of \finsp.

@@

\begin{theorem}[Unforgeability-1 of \CUASMPS]
  If the base \CUASGen construction is unforgeable according to
  \defref{def:forge-uas}, then \CUASMPS satisfies unforgeability-1 as
  defined in \cite{ngsy22}.
\end{theorem}
